A Horrocks-type theorem for even orthogonal $K_2$

### 2020-09-23 dl-paper.tex
Second version submitted to arxiv
Fix links on arxiv
Fix misprint

\documentclass[oneside, 8pt]{amsart}
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[hyperref=true, backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[breaklinks=false,unicode]{hyperref}
\definecolor{DarkPurple}{rgb}{0.40,0.0,0.20}
\hypersetup{colorlinks=true,citecolor=NavyBlue,linkcolor=DarkPurple,urlcolor=NavyBlue}
\usepackage{color} 
\usepackage[capitalize]{cleveref}
\usepackage{tikz,tikz-cd}
\usepackage{enumitem}

@@

For a subset of roots $U \subseteq \Phi$ we denote by $\mathcal{Z}(U, R, I)$ the subset of roots consisting of elements $x_\alpha(s)$, $s \in I$, $\alpha \in \Phi$ and $z_\alpha(s, \xi)$, $\alpha \in U$, $s\in I$, $\xi \in R$.
\begin{externaltheorem}[Stepanov] \label{thm:Stepanov} 
Let $S \subseteq \Phi$ be a parabolic subset of $\Phi$. Then the group $\overline{\St}(\Phi, R, I)$ is generated by the set $\mathcal{Z}(\Sigma_S, R, I)$.
 \end{externaltheorem} \begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}

>>>>

\documentclass[oneside, 8pt]{amsart}
\pdfoutput=1
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[hyperref=true, backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[breaklinks=true,unicode]{hyperref}
\definecolor{DarkPurple}{rgb}{0.40,0.0,0.20}
\hypersetup{colorlinks=true,citecolor=NavyBlue,linkcolor=DarkPurple,urlcolor=NavyBlue}
\usepackage{color} 
\usepackage[capitalize]{cleveref}
\usepackage{tikz,tikz-cd}
\usepackage{enumitem}

@@

For a subset of roots $U \subseteq \Phi$ we denote by $\mathcal{Z}(U, R, I)$ the set consisting of elements $x_\alpha(s)$, $s \in I$, $\alpha \in \Phi$ and $z_\alpha(s, \xi)$, $\alpha \in U$, $s\in I$, $\xi \in R$.
\begin{externaltheorem}[Stepanov] \label{thm:Stepanov} 
Let $S \subseteq \Phi$ be a parabolic subset of $\Phi$. Then the group $\overline{\St}(\Phi, R, I)$ is generated by the set $\mathcal{Z}(\Sigma_S, R, I)$.
 \end{externaltheorem} \begin{proof} See~\cite[Lemma~4]{S15}. \end{proof}
